Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-19 main.tex
:pencil: Update achievable rates

	\emph{Notations:} Scalars, vectors and matrices are respectively denoted by italic, bold lower-case, and bold upper-case letters.
	$j$ represents the imaginary unit.
	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
	% $\boldsymbol{I}$ represents the identity matrix.
	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1} \mid \sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
	% $\odot$ denotes the Hadamard product.
	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
	$\sim$ means ``distributed as''.
	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
\end{section}

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of backscatter symbols
		\begin{subequations}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
			\label{eq:equivalent_channel}
		\end{subequations}
		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{\Gamma_1,\ldots,\Gamma_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all Metascatters.

@@

		where $x_{m_k}$ and $x_{m_\mathcal{K}}$ are the symbol and symbol set associated with state $m_k$ and state set $m_{\mathcal{K}}$, respectively.%

@@

			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},

@@

			\resizebox{0.95\columnwidth}{!}{

@@

			P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,

@@

		\begin{remark}
			% For a general input distribution, not only the optimal decision thresholds
			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
			% Next, we will restrict the design over convex decision regions.
			Next, we will constrain the decision regions to convex and consider suboptimal threshold design accordingly.
			% Hence,
			% threshold design papers are constrained to convex quantizer, we may end up using a similar assumption.
			% decision region design to convex

			% design over convex decision regions.

			% decision regions are first restricted to convex

			% The question was answered in \cite{Qian2019b,Nguyen2021b} only for single source with binary inputs.

			% Even for a single source with non-binary inputs,

			% For a general input distribution, not only the rate-optimal decision thresholds
			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
		\end{remark}

		% divide the accumulated energy $z$ into disjoint decision regions.
		% where $x_{m_k}$ is the backscatter symbol associated with state $m_k$ and $x_{m_\mathcal{K}}$ is
		% and $x_{m_\mathcal{K}}$ are the backscatter symbols associated with state $m_k$ and $m_{\mathcal{K}}$, respectively.

		% At primary block $n$, the received signal

		% Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
		% Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
		% Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
		% Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
		% \begin{equation}
		% 	\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
		% 	\label{eq:receive_variance}
		% \end{equation}

		% Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
		% Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
		% \begin{equation}
		% 	f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
		% 	\label{eq:energy_distribution}
		% \end{equation}

		% Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
		% To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
		% \begin{equation}
		% 	P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
		% 	\label{eq:dtmac}
		% \end{equation}
		% where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
		Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
		\begin{equation}
			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})$.
		Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information_function}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Therefore, the backscatter mutual information is
		\begin{equation}
			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
			\label{eq:backscatter_mutual_information}
		\end{equation}

		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
		% TODO notation
		\begin{equation}
			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
			\label{eq:primary_marginal_information_function}
		\end{equation}
		and the primary (ergodic) mutual information is
		\begin{equation}
			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			\label{eq:primary_mutual_information}
		\end{equation}

>>>>

	\emph{Notations:} Scalars, vectors and matrices are respectively denoted by italic, bold lower-case, and bold upper-case letters.
	$j$ represents the imaginary unit.
	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
	% $\boldsymbol{I}$ represents the identity matrix.
	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1}|\sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
	% $\odot$ denotes the Hadamard product.
	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
	$\sim$ means ``distributed as''.
	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
\end{section}

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all Metascatters.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of backscatter symbols
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
		\end{subequations}
		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{\Gamma_1,\ldots,\Gamma_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

		% At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ collect the state indexes of all Metascatters.
		At a specific backscatter block, denote $m_k \in \mathcal{M}$ as the state index of Metascatter $k$, and let $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all Metascatters.

@@

		where $x_{m_k}$ and $x_{m_\mathcal{K}}$ are the symbol and symbol tuple associated with state $m_k$ and state tuple $m_{\mathcal{K}}$, respectively.%

@@

			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},

@@

			\resizebox{0.9\columnwidth}{!}{

@@

			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \dd z,

@@

		\begin{remark}
			% For a general input distribution, not only the optimal decision thresholds
			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
			% Next, we will restrict the design over convex decision regions.
			Next, we will constrain all decision regions to convex and consider suboptimal threshold design accordingly.
			% For a general input distribution, not only the rate-optimal decision thresholds
			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
		\end{remark}
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(\Gamma_1),\ldots,P_k(\Gamma_M)]^T \in \mathbb{R}^{M \times 1}$. With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			% I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information_function}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Moreover, we can write the backscatter mutual information as
		\begin{equation}
			% I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
			I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}. We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		% \begin{equation}
		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
		% 	\label{eq:primary_information_function}
		% \end{equation}
		\begin{equation}
			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		% the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I^{\mathrm{P}}_{k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information_function}
		\end{equation}
		and the primary ergodic mutual information as
		% and the primary (ergodic) mutual information is
		\begin{equation}
			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}

		% Moreover, with $\rho \in [0,1]$ being the relative priority of the primary link, we define corresponding weighted sum information function, marginal information, and mutual information respectively as
		Finally, with a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I^{\mathrm{P}}_{k}(s;y|x_{m_k}) + (1 - \rho) I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                 \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in [0,1]$ is the relative priority of the primary link.
